% Rei Doda — CV
\documentclass[10pt,a4paper]{article}

% ---------- Geometry ----------
\usepackage[a4paper,top=18mm,bottom=18mm,left=18mm,right=18mm]{geometry}

% ---------- Fonts ----------
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{lmodern}
\else
  \usepackage{fontspec}
  \IfFontExistsTF{Inter}{
    \setmainfont{Inter}[
      UprightFont = * Regular,
      BoldFont    = * SemiBold,
      ItalicFont  = * Italic
    ]
  }{
    \setmainfont{TeX Gyre Heros} % Fallback font
  }
\fi

\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\definecolor{ink}{HTML}{111111}
\definecolor{muted}{HTML}{6B6B6B}
\definecolor{hair}{HTML}{E6E6E6}

\hypersetup{
  colorlinks=true,
  linkcolor=ink,
  urlcolor=ink
}

% ---------- Spacing / rhythm ----------
\usepackage{parskip}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\usepackage{setspace}
\setstretch{1.05}

% ---------- Lists ----------
\usepackage{enumitem}
\setlist[itemize]{leftmargin=15pt,itemsep=2.5pt,topsep=2pt}

% ---------- Section formatting ----------
\usepackage{titlesec}
\titleformat{\section}
  {\color{muted}\bfseries\fontsize{10.25pt}{12.5pt}\selectfont}
  {}{0pt}{\MakeUppercase}
\titlespacing*{\section}{0pt}{14pt}{6pt}

% ---------- Tables / alignment ----------
\usepackage{tabularx}
\usepackage{needspace}

% ---------- Prevent orphan section titles ----------
\usepackage{etoolbox}
% Guarantees space for a section title + a few lines after it
\pretocmd{\section}{\needspace{6\baselineskip}}{}{}

% ---------- Skill chips (transparent square buttons) ----------
\usepackage{tikz}
\newcommand{\skill}[1]{%
  \tikz[baseline=(X.base)]\node[
    draw=hair,
    line width=0.35pt,
    rounded corners=2.2pt,
    inner xsep=5.5pt,
    inner ysep=2.25pt,
    fill=hair,
    fill opacity=0.18,
    text opacity=1
  ] (X) {\fontsize{9.2pt}{11pt}\selectfont\color{ink}#1};%
}
% Break-friendly spacing between chips (allows line wrap)
\newcommand{\skillgap}{\hspace{4pt}\allowbreak}

% ---------- Hairline divider ----------
\newcommand{\hairline}{%
  \vspace{6pt}%
  {\color{hair}\hrule height 0.35pt}%
  \vspace{10pt}%
}

% ---------- Typography helpers ----------
\newcommand{\meta}[1]{{\color{muted}\fontsize{9.4pt}{12pt}\selectfont #1}}
\newcommand{\smallmeta}[1]{{\color{muted}\fontsize{9.0pt}{11.5pt}\selectfont #1}}
\newcommand{\roleline}[3]{%
  \textbf{#1}\hfill{\meta{#2}}\\[-1pt]
  \smallmeta{#3}%
}
\newcommand{\projhead}[1]{\textbf{#1}}
\newcommand{\projmeta}[1]{\smallmeta{#1}}

% ---------- Left label width (for perfectly aligned blocks) ----------
\newcommand{\LabelW}{28mm}

% Aligned label-value row
\newcommand{\kv}[2]{%
  \begin{tabularx}{\textwidth}{@{}p{\LabelW}X@{}}%
  \meta{#1} & #2%
  \end{tabularx}%
}

% Skill row (raggedright helps chips wrap nicely)
\newcommand{\skillrow}[2]{%
  \begin{tabularx}{\textwidth}{@{}p{\LabelW}X@{}}%
  \meta{#1} & \raggedright #2%
  \end{tabularx}%
}

% Optional: reduce widows/orphans even more
\clubpenalty=10000
\widowpenalty=10000
\displaywidowpenalty=10000

\begin{document}
\color{ink}

% ===================== HEADER =====================
{\fontsize{24pt}{28pt}\selectfont\textbf{Rei Doda}}\\[-1pt]
{\fontsize{12pt}{15pt}\selectfont\color{muted}Software Developer}

\vspace{8pt}
\meta{Europe (Italy / Albania) \,·\,
\href{mailto:reidoda@icloud.com}{reidoda@icloud.com} \,·\,
\href{https://www.linkedin.com/in/rei-doda}{linkedin.com/in/reiidoda} \,·\,
\href{https://github.com/reiidoda}{github.com/reiidoda}}

\hairline

% ===================== SUMMARY =====================
\section{Summary}
Interested in Artificial Intelligence and Neuroscience.
Experienced with Python, Java, and C/C++, applied AI (RAG, OCR, LLM integration), and full-stack architectures.

\hairline

% ===================== EXPERIENCE =====================
\section{Experience}

\needspace{8\baselineskip}
\roleline{Mövenpick Hotel (Accor Group) — IT Officer}{Jul 2023 – Jun 2025}{Durrës, Albania}
\begin{itemize}
  \item Built a Human Resources (HR) application for employee management, attendance/leave workflows, approvals, and role-based access.
  \item Developed a parking payment application with ticket/plate validation, online payments, receipt generation, and administrative reporting.
  \item Managed enterprise IT infrastructure including servers, networking equipment, POS systems, and workstations.
  \item Provided cross-department technical support focused on uptime, reliability, and fast resolution.
  \item Enforced security policies, backups, and compliance aligned with Accor Group standards.
  \item Performed monitoring, updates, and preventative maintenance to ensure operational continuity.
\end{itemize}

\needspace{9\baselineskip}
\roleline{Upnova Group S.r.l — Lead Software Developer}{Oct 2022 – Aug 2024}{Bari, Italy}
\begin{itemize}
  \item Led development of AI-powered web applications using Python-based architectures.
  \item Designed and deployed ML pipelines integrated into backend services and APIs.
  \item Implemented OCR and NLP workflows for automated document processing and extraction.
  \item Built RAG-based virtual assistants for intelligent document retrieval and contextual responses.
  \item Focused on maintainable system design, performance, and production readiness.
\end{itemize}

\needspace{8\baselineskip}
\roleline{Genesys Software S.r.l — Software Developer}{Nov 2021 – May 2022}{Bari, Italy}
\begin{itemize}
  \item Developed high-performance software in C/C++ with emphasis on algorithmic efficiency and memory control.
  \item Implemented real-time algorithms (e.g., pathfinding, resource allocation) for system-level operations.
  \item Integrated low-level modules with broader systems and IoT environments for reliable performance.
  \item Worked with Boost and OpenCV in performance-critical contexts.
\end{itemize}

\needspace{8\baselineskip}
\roleline{Vallefiorita — Software Developer}{Sep 2020 – Jul 2021}{Bari, Italy}
\begin{itemize}
  \item Developed machine learning and computer vision models using TensorFlow, PyTorch, and OpenCV.
  \item Built end-to-end AI pipelines: data acquisition, preprocessing, inference, and deployment.
  \item Deployed solutions on edge/IoT devices with performance optimization and monitoring integration.
  \item Collaborated with cross-functional stakeholders to translate requirements into deployable AI features.
\end{itemize}

\hairline

% ===================== PROJECTS =====================
\section{Projects}

\needspace{9\baselineskip}
\projhead{Examen — AI-Powered Examination Platform}\\[-1pt]
\projmeta{Stack: Angular SSR · Spring Boot · PostgreSQL · Docker · JWT · Flyway}\\
\projmeta{Repo: \href{https://github.com/reiidoda/examen}{github.com/reiidoda/examen}}
\begin{itemize}
  \item Designed and implemented a full-stack platform for AI-assisted examination workflows.
  \item Built Spring Boot REST APIs secured with JWT-based authentication and authorization.
  \item Implemented database schema versioning and migrations using Flyway.
  \item Developed an Angular SSR frontend for structure, performance, and scalability.
  \item Added API documentation and observability via Swagger/OpenAPI and Actuator-style health checks.
  \item Containerized services with Docker for reproducible development and deployment.
\end{itemize}

\needspace{9\baselineskip}
\projhead{Thinking in Code — AI Knowledge \& Processing Platform}\\[-1pt]
\projmeta{Stack: FastAPI · Worker pipelines · RAG · Vector search · Docker Compose}\\
\projmeta{Repo: \href{https://github.com/reiidoda/thinking_in_code}{github.com/reiidoda/thinking\_in\_code}}
\begin{itemize}
  \item Designed a modular system for structured knowledge processing and AI-driven content generation.
  \item Implemented FastAPI services with background workers and job lifecycle/status tracking.
  \item Built retrieval-augmented generation pipelines with vector search (e.g., Chroma/FAISS).
  \item Integrated multiple LLM backends (local and hosted) with configurable providers.
  \item Orchestrated services using Docker Compose for reproducible environments.
\end{itemize}

\needspace{6\baselineskip}
\projhead{Battleship Game}\\[-1pt]
\projmeta{Stack: Java · Gradle · Docker}
\begin{itemize}
  \item Implemented a two-player strategy game in Java with clean structure and reproducible execution.
  \item Containerized the application using Docker for consistent runtime behavior.
\end{itemize}

\needspace{5\baselineskip}
\projhead{Hyerun of History}\\[-1pt]
\projmeta{Stack: C}
\begin{itemize}
  \item Developed a text-based adventure game emphasizing control flow, state handling, and logic.
\end{itemize}

\needspace{5\baselineskip}
\projhead{Biblioteca Poggiolevante}\\[-1pt]
\projmeta{Stack: PHP · Web}
\begin{itemize}
  \item Built a virtual library system enabling search, browsing, and ordering of books in a college library.
\end{itemize}

\hairline

% ===================== VOLUNTEERING =====================
\section{Volunteering}

\needspace{7\baselineskip}
\roleline{EG Global — Ambassador}{Dec 2021 – Jan 2025}{Worldwide}
\begin{itemize}
  \item Supported non-profits and social entrepreneurs through coordination, promotion, and community engagement.
  \item Contributed to initiatives focused on transparent impact and accessible collaboration.
\end{itemize}

\needspace{7\baselineskip}
\roleline{Fondazione Giovanni Paolo II ETS — Student Teacher}{Nov 2021 – May 2024}{Bari, Italy}
\begin{itemize}
  \item Taught introductory Python programming with focus on computational thinking and problem-solving.
  \item Helped students build confidence with code through structured exercises and clear explanations.
\end{itemize}

\hairline

% ===================== EDUCATION & LANGUAGES =====================
\section{Education}
\kv{}{ \textbf{BSc in Computer Science} — University of Bari "Aldo Moro", Bari, Italy }

\section{Languages}
\kv{}{Albanian (Native) · Italian (Full professional proficiency) · English (Full professional proficiency)}

\hairline

% ===================== SKILLS (Chips) =====================
\section{Skills}

\skillrow{Languages}{
  \skill{Python}\skillgap
  \skill{Java (JDK 25)}\skillgap
  \skill{TypeScript}\skillgap
  \skill{C}\skillgap
  \skill{C++}\skillgap
  \skill{SQL}
}

\skillrow{Frontend}{
  \skill{Angular (SSR)}\skillgap
  \skill{SCSS}\skillgap
  \skill{Node.js}\skillgap
  \skill{npm}
}

\skillrow{Backend}{
  \skill{Spring Boot}\skillgap
  \skill{FastAPI}\skillgap
  \skill{REST API design}\skillgap
  \skill{SSE}
}

\skillrow{Security}{
  \skill{JWT auth}\skillgap
  \skill{Authorization}\skillgap
  \skill{Secure API design}
}

\skillrow{Databases}{
  \skill{PostgreSQL}\skillgap
  \skill{Relational modeling}\skillgap
  \skill{Flyway migrations}
}

\skillrow{AI}{
  \skill{RAG}\skillgap
  \skill{Vector search}\skillgap
  \skill{Chroma}\skillgap
  \skill{FAISS}\skillgap
  \skill{OCR pipelines}\skillgap
  \skill{LLM integration}
}

\skillrow{Async}{
  \skill{Worker pipelines}\skillgap
  \skill{Background jobs}\skillgap
  \skill{Status tracking}\skillgap
  \skill{Artifact generation}
}

\skillrow{DevOps}{
  \skill{Linux}\skillgap
  \skill{Docker}\skillgap
  \skill{Docker Compose}\skillgap
  \skill{Nginx}\skillgap
  \skill{Bash}
}

\skillrow{Obs.}{
  \skill{Swagger/OpenAPI}\skillgap
  \skill{Spring Actuator}\skillgap
  \skill{Structured logging}
}

\skillrow{Soft skills}{
  \skill{Time management}\skillgap
  \skill{Communication}\skillgap
  \skill{Technical leadership}\skillgap
  \skill{Cross-team collaboration}\skillgap
  \skill{Mentoring}\skillgap
  \skill{Teamwork}\skillgap
  \skill{Problem solving}
}

\end{document}